Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-02-04 supplement.tex
missed on caption

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-csfs-continuous-migration.pdf}
    \caption{
        \textbf{Conditional SFS compared to continuous-migration model.}
    }
    \label{fig:supp-csfs-continuous-migration}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-csfs-continuous-migration.pdf}
    \caption{
        \textbf{Conditional SFS compared to continuous-migration model.}
        The continuous-migration model provides a better fit to the data than
        either the single-origin model or the merger-without-stem-migration
        model, although systematic deviations are still noticeable in each
        population.
    }
    \label{fig:supp-csfs-continuous-migration}
\end{figure}
